Topic modeling on EU and the USA research projects

### 2017-06-11 thesis_report/draft_thesis.tex
Fixed: "Some probability concepts" subsection in Theoretic background

\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{cite}
\usepackage{algorithm2e}

@@

Many applications of if topic modeling also eliminate from the vocabulary so-
called “stop” words. These are words that are common in most documents and do
not correspond to any particular subject matter. They include pronouns (you,
he, it), connectives (and, because, however), prepositions (to, of, before),
and auxiliaries (have, been, can, should). Stop words may also include generic
nouns (amount, part, nothing) and verbs (do, have). A collection of documents
is represented as a two-dimensional matrix where each row describes a document
and each column corresponds to a word. Each entry in this matrix is an integer
count; most entries are zero. It makes sense to view each column as a feature.

@@

Once we have a representation for individual documents, the natural next step
is to select a model for a set of documents. It is important to understand the
difference between a representation and a model. A representation is a way of
encoding an entity as a data structure. A model is an abstraction of a set of
entities, for example a probability distribution. Given a training set of
documents, we will choose values for the parameters of a probabilistic model
that make the training documents have high probability. Then, given a test
document, we can evaluate its probability according to the model. The higher
this probability is, the more similar the test document is to the training set.

The probability distribution that we use is the multinomial. Mathematically,
this distribution is:

@@

where the data $x$ are a vector of non-negative integers and the parameters
$\theta$ are a real-valued vector. Both vectors have the same length $m$.
Intuitively, $\theta_j$ is the probability of word $j$ while $x_j$ is the count
of word $j$. Each time word $j$ appears in the document it contributes an amount
$\theta_j$ to the total probability, hence the term $\theta_j^{x_j}$. The
components of $\theta$ are non-negative and have unit $\sum\limits_{j=1}^m
\theta_j = 1$. A vector with these properties is called a unit vector.

@@

The Dirichlet process is a way to model randomness of a probability mass
function (PMF) with unlimited options (e.g. an unlimited amount of dice in a
bag). The process is similar Polya’s Urn, only instead of having a set number
of ball colors you have an unlimited amount:

>>>>

\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{cite}
\usepackage{algorithm2e}
\usepackage{url}

@@

Many applications of topic modeling also eliminate from the vocabulary so-
called “stop” words. These are words that are common in most documents and do
not correspond to any particular subject matter. They include pronouns (you,
he, it), connectives (and, because, however), prepositions (to, of, before),
and auxiliaries (have, been, can, should). Stop words may also include generic
nouns (amount, part, nothing) and verbs (do, have). A collection of documents
is represented as a two-dimensional matrix where each row describes a document
and each column corresponds to a word. Each entry in this matrix is an integer
count; most entries are zero. It makes sense to view each column as a feature.

@@

Once we have a representation for individual documents, the natural next step
is to select a model for a set of documents. Given a training set of
documents, we will choose values for the parameters of a probabilistic model
that make the training documents have high probability. Then, given a test
document, we can evaluate its probability according to the model. The higher
this probability is, the more similar the test document is to the training set.

The probability distribution that we use is the multinomial. In probability 
theory, the multinomial distribution is a generalization of the binomial 
distribution. For example, it models the probability of counts for rolling 
a k-sided dice n times. For n independent trials each of which leads to a 
success for exactly one of k categories, with each category having a given 
fixed success probability, the multinomial distribution gives the 
probability of any particular combination of numbers of successes for the 
various categories \footnote{\url{https://en.wikipedia.org/wiki/Multinomial_distribution}}.

Mathematically, this distribution is:

@@

where the data $x$ are a vector of non-negative integers and the parameters
$\theta$ are a real-valued vector. Both vectors have the same length $m$.
Intuitively, $\theta_j$ is the probability of word $j$ while $x_j$ is the count
of word $j$. Each time word $j$ appears in the document it contributes an amount
$\theta_j$ to the total probability, hence the term $\theta_j^{x_j}$. The
components of $\theta$ are non-negative and have unit $\sum\limits_{j=1}^m
\theta_j = 1$.

@@

The Dirichlet process is a way to model randomness of a probability mass
function (PMF) with unlimited options (e.g. an unlimited amount of dice in a
bag). The process is similar Polya’s Urn \footnote{\url{http://www.statisticshowto.com/dirichlet-distribution/}}, only instead of having a set number
of ball colors you have an unlimited amount:
